Textmining in Economics

### 2017-10-14 textm.Rmd
new

This gives the following Document-Term-Matrix
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tm)

@@

***
Now we set the model parameter

```{r, include=FALSE}
library(lda)

@@

```{r, echo=FALSE}
ldaModel <- lda.collapsed.gibbs.sampler(corpusLDA$documents,K=2,vocab=corpusLDA$vocab,burnin=9999,num.iterations=100000,alpha=0.8,eta=0.1)

>>>>

***
This gives the following Document-Term-Matrix
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tm)

@@

```{r, eval=FALSE}
library(lda)

@@

```{r, eval=FALSE}
ldaModel <- lda.collapsed.gibbs.sampler(corpusLDA$documents,K=2,vocab=corpusLDA$vocab,burnin=9999,num.iterations=100000,alpha=0.8,eta=0.1)
